---
title: "Introduction to tmbExtract"
author: "Jemay Salomon"
date: "`r format(Sys.time(), '%d/%m/%Y')`"
lang: "fr"
output:
  html_document:
    toc: true
    toc_depth: 5
    toc_float: true
    number_sections: TRUE
  pdf_document:
    toc: true
    toc_depth: 3
    number_sections: TRUE
colorlinks: true
urlcolor: blue
abstract: "This document aims at introducing the package tmbExtract and show to extract parameters from TMB output."
vignette: >
  %\VignetteIndexEntry{Example}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

This document will also require external packages to be available, for instance:

```{r load_pkg}
suppressPackageStartupMessages(library(MASS))
suppressPackageStartupMessages(library(rutilstimflutre))
suppressPackageStartupMessages(library(TMB))
suppressPackageStartupMessages(library(dplyr))
suppressPackageStartupMessages(library(gtools))
suppressPackageStartupMessages(library(ggplot2))
suppressPackageStartupMessages(library(mvtnorm))
suppressPackageStartupMessages(library(MixMatrix))
suppressPackageStartupMessages(library(Matrix))
suppressPackageStartupMessages(library(lme4))
suppressPackageStartupMessages(library(Rcpp))
#devtools::install_github("kaskr/TMB_contrib_R/TMBhelper")
suppressPackageStartupMessages(library(TMBhelper))


```

Execution time (see the appendix):
```{r time_0}
t0 <- proc.time()
```


# Overview
This script aims to simulate three (3) breeding strategy scenarios for interspecific mixed crops using wheat and pea as species models, considering a range of parameters. The simulation involves 150 wheat plants (focal) and 1 tester pea and three (3) experimental designs

* Description

200 wheats in pure  
2 tester pea in pure stand  
400 mixed stands (200-wheats x 2-peas)   
X 2 blocs = 1204 microplots


# Simulation : general data structure

## Loading functions and set contrast for inferences
```{r}
srcDir <- file.path(projectDir, "src/")
source(paste0(srcDir, "phdmobidiv_utils.R")) # loading functions
```

```{r}
options(contrasts=c("contr.sum", "contr.poly"))
getOption("contrasts")
```


## Dimensions of the simulation
```{r}
# Plant materials
W = 200 #number of wheat genotypes
P = 2 # Number of pea genotypes
wheats <- sprintf("wheat%02d", 1:W) # creates names for W wheat genotypes 
peas <- sprintf("pea%02d", 1:P) # creates names for P pea genotypes 

# levels
levSpecies <- c("wheat", "pea")
levStand <- c("pure", "mixed")
levContrast <- c("mu","block1")
levelsPea <- peas
```


## Set-up the initial data frame
```{r}
## blocks
B <- 2 #number of blocks
blocks <- LETTERS[1:B] # creates names for B
levblocks <- blocks

## creates the data structure
dat.block1 <- data.frame(stand=c(rep("pure",W),
                                 rep("pure",P),
                                 rep("mixed",W*P)),
                         wheat=c(wheats, rep(NA, P), rep(wheats, each=P)),
                         pea=c(rep(NA, W),peas, rep(peas, W)),
                         block=NA)
dat <- dat.block1

## format
for(k in 2:B){ # attaches the the same data.frame underneath k-times
  dat <- rbind(dat, dat.block1)
}
dat$block <- as.factor(rep(blocks, each=nrow(dat.block1)))
dat$name <- paste0(dat$wheat, "_", dat$pea)
dat$name <- gsub("NA_|_NA", "", dat$name)
dat$name <- factor(dat$name)
dat$stand=as.factor(dat$stand)
str(dat)
n.bl=length(unique(dat$name))
nb=length(unique(dat$block))
dat$x=c(rep(1, n.bl), rep(2,n.bl))
dat$y=c(replicate(nb, sample(1:n.bl)))
```

```{r}
dat_m <- dat #to use later in section mix only
```


## Reformatting

```{r}
## splitDat
datTest=SplitDAT(df=dat, name="name", stand="stand", block="block", list.pea=peas,
                 sep="_")
datTest$focal <- factor(datTest$focal)
datTest$neighbors <- factor(datTest$neighbors)
datTest$species <- factor(datTest$species, levels=c("wheat","pea"))
datTest$block<- factor(datTest$block, levblocks)
str(datTest)
head(datTest)
tail(datTest)
```


## Params for fixed effects

In this section we set up the parameters for simulations

Here the mean of yield for wheat and pea in pure and mixed stand
```{r}
mu_w_pur=65
mu_w_mix = 65*0.75
mu_p_pur =30
mu_p_mix = 30*1.0

```


Block effects v1: `~ 0 + species + species:block`
Seeting up the fixed parameters for block effects using  `contr.sum`

```{r}
## contrast block1-Species array
block1SpeciesEffs <- array(0,
                           dim = c(length(levSpecies), 
                                   length(levStand), 
                                   length(levContrast)),
                           dimnames = list(levContrast, 
                                           levStand,levSpecies ))
block1SpeciesEffs["mu",,"wheat"] <- c(mu_w_pur, mu_w_mix)
block1SpeciesEffs["mu",,"pea"] <- c(mu_p_pur, mu_p_mix)
block1SpeciesEffs["block1",,"wheat"] <- c(1.3, -0.5)
block1SpeciesEffs["block1",,"pea"] <- c(-0.7, 0.4)
block1SpeciesEffs


B_mix <- block1SpeciesEffs[,"mixed",]


#matrix of DGE and IGE pea01
focal1 <- 7  # DGE.pea01
neighbors1  <- -2 # IGE.pea01
U_p <- matrix(c(
  neighbors1, 0,
  0, focal1
), ncol = 2)
colnames(U_p) <- c("neighbors1", "focal1")

#check
true_beta = c(c(block1SpeciesEffs["mu","pure","wheat"],
             block1SpeciesEffs["block1","pure","wheat"]), 
             c(block1SpeciesEffs["mu","pure","pea"],
             block1SpeciesEffs["block1","pure","pea"], focal1),
             neighbors1, c(B_mix))
U_p
B_mix
true_beta
```


## Params for random effects :

In thi section we setting up parameters for the random effects
```{r}
truth <- list()
## wheat
truth[["sigma2.DGEw"]] = 5^2 # values ---> +/-(2*5)
truth[["h2_DGEw"]]= 0.7 # test 0.1 à 0.9
truth[["h2_DGEp"]] = 0.75 # test 0.1 à 0.9
truth[["sigma2.DGEp"]] = 4.5^2
truth[["sigma2.IGEp"]] = 0.30*truth[["sigma2.DGEp"]]

## error variances
truth[["sigma2_err_w"]] <- ((1 - truth[["h2_DGEw"]] ) /truth[["h2_DGEw"]]) * truth[["sigma2.DGEw"]]
truth[["sigma2_err_p"]] <- ((1 - truth[["h2_DGEp"]] ) /truth[["h2_DGEp"]]) * truth[["sigma2.DGEp"]]
```


# Simulate data
```{r}
listZs <- list()
```


##  Pure only

### format dat
```{r}
#dat
dat_pur <- droplevels(datTest[datTest$stand=="pure", ])
rownames(dat_pur)<- NULL

#dat_pea_pur
dat_pea_pur<- droplevels(dat_pur[dat_pur$species=="pea", ])
dat_pea_pur$focal <- factor(dat_pea_pur$focal, levels=levelsPea)
dat_pea_pur$neighbors <- factor(dat_pea_pur$neighbors, levels=levelsPea)
rownames(dat_pea_pur)<- NULL

#dat_wheat_pur
dat_wheat_pur <- droplevels(dat_pur[dat_pur$species=="wheat", ])
rownames(dat_wheat_pur)<- NULL
```


```{r}
# incidence matrix
getOption("contrasts")
options(contrasts=c("contr.sum", "contr.poly"))

#wheat
listZs[["X_wheat_pur"]] <- model.matrix(~1+block, data = dat_wheat_pur)
dim(listZs[["X_wheat_pur"]])
colnames(listZs[["X_wheat_pur"]])

#pea
listZs[["X_pea_pur"]]<- model.matrix(~1+block+focal, data = dat_pea_pur)
dim(listZs[["X_pea_pur"]])
colnames(listZs[["X_pea_pur"]])

```



### yield

`wheat`

```{r}
set.seed(1234)
K = diag(W)


## errors
Idn_w_pur <- diag(nrow(dat_wheat_pur))
R <- truth[["sigma2_err_w"]] *Idn_w_pur
e <- mvrnorm(n=1, mu=rep(0,nrow(dat_wheat_pur)), Sigma=R) 

## Yiel ~Fixed + DGE + e
y_w_pur_1 <- listZs[["X_wheat_pur"]] %*% c(block1SpeciesEffs["mu","pure","wheat"],
             block1SpeciesEffs["block1","pure","wheat"]) + e
y_w_pur_1<- y_w_pur_1[,1]
dat_wheat_pur$yield_1 <- y_w_pur_1


#check
head(dat_wheat_pur)
```


`pea`

```{r}
set.seed(1234)
## errors
Idn_p_pur <- diag(nrow(dat_pea_pur))
R <- truth[["sigma2_err_p"]] *Idn_p_pur
e <- mvrnorm(n=1, mu=rep(0,nrow(dat_pea_pur)), Sigma=R) 

## Yiel ~Fixed + e
y_p_pur_1 <- listZs[["X_pea_pur"]] %*% c(block1SpeciesEffs["mu","pure","pea"],
             block1SpeciesEffs["block1","pure","pea"], focal1) + e
y_p_pur_1<- y_p_pur_1[,1]
dat_pea_pur$yield_1 <- y_p_pur_1
summary(lm(yield_1~1+block+focal, data = dat_pea_pur))
sigma(lm(yield_1~1+block+focal, data = dat_pea_pur))
```


##  Mix only

### format dat

```{r}
dat_mix <-droplevels(dat_m[dat_m$stand=="mixed",])
dat_mix$pea <- as.factor(dat_mix$pea)
dat_mix$wheat <- as.factor(dat_mix$wheat)
str(dat_mix)
rownames(dat_mix)<- NULL
# Sort the dataframe
dat_mix <- dat_mix %>% arrange(pea, block)
str(dat_mix)
```


```{r}
set.seed(1234)

## format
d <- length(levSpecies)
p <- length(levblocks) ;
m <- length(unique(dat_mix$name)); 
species_plot<- unique(dat_mix$name) #number of mixed plots per species
n_1 <- p * m
n_2 <- n_1 * d

stopifnot(all(dim(B_mix) == c(p, d)))
truth[["B_mix"]] <- B_mix
b_mix <- c(B_mix)

names(b_mix) <- paste(rep(rownames(B_mix),ncol(B_mix)),
                      rep(colnames(B_mix), each=nrow(B_mix)),
                      sep="_")
b_mix



listZs[["Xmix"]] <- model.matrix(~ 1 + block, dat_mix, list(block="contr.sum"))
stopifnot(all(dim(listZs[["Xmix"]]) == c(n_1, p)))
head(listZs[["Xmix"]])


## Errors:
M_E <- matrix(0, n_1, d,
              dimnames=list(NULL, levSpecies))
Id_n1 <- diag(n_1)
truth[["cor_E"]]<- -0.2
Sigma_E <- matrix(c(truth[["sigma2_err_w"]], NA, NA, truth[["sigma2_err_p"]]), 2, 2)
Sigma_E[1,2] <- Sigma_E[2,1] <- truth[["cor_E"]] * sqrt(Sigma_E[1,1] * Sigma_E[2,2])
cov_Er <- truth[["cor_E"]] * sqrt(Sigma_E[1,1] * Sigma_E[2,2])
dimnames(Sigma_E) <- list(levSpecies, levSpecies)
truth[["Sigma_E"]] <- Sigma_E
E <- rmatnorm(n=1, M_E, U=Id_n1, V=Sigma_E)
R <- Sigma_E %x% diag(n_1)


## matrix 2
X_2 <- diag(d) %x% listZs[["Xmix"]]
stopifnot(all(dim(X_2) == c(n_2, d*p)))

```


### design matrix
```{r}
listZs[["ZDp_mix"]] <-cbind(model.matrix(~1+pea, data=dat_mix)[, -1],model.matrix(~1+pea, data=dat_mix)[, -1])
colnames(listZs[["ZDp_mix"]]) <- c("neigborhs1", "focal1")
```


### format dat_mix
```{r}
## concat Y_mix or use y_mix
wheat_dat <- dat_mix
wheat_dat$species <-"wheat"
pea_dat <- dat_mix
pea_dat$species <-"pea"
dat_mix <-rbind(wheat_dat, pea_dat)
dat_mix$species <- factor(dat_mix$species, levels=c("wheat","pea"))
dat_mix$wheat <-as.factor(dat_mix$wheat)
dat_mix$pea <-as.factor(dat_mix$pea)
rownames(dat_mix)<- NULL

```


### yield 

yield (Y_mix_1)/Mod 1 : fixed effects + wheat DGE-IGE + E
```{r}
Y_mix_1 <- listZs[["Xmix"]] %*% B_mix + listZs[["ZDp_mix"]]%*%U_p+ E[,,1]
colnames(Y_mix_1) <- c("yield.wheat", "yield.pea")
y_mix_1 <- c(Y_mix_1)
dat_mix$yield_1 <-y_mix_1
head(Y_mix_1)
```




# Inferences

## pure

### lmer :: Model 1 (Fixed effects + DGE + e)

```{r}
mod_w_pur <- lm(yield_1~1+block, data = dat_wheat_pur)
mod_p_pur <- lm(yield_1~1+block+focal, data = dat_pea_pur)

cbind("true"=c("specieswheat_pur"=block1SpeciesEffs["mu", "pure", "wheat"], 
               "specieswheat:block1_pur"=block1SpeciesEffs["block1", "pure", "wheat"],
               "speciespea"=block1SpeciesEffs["mu", "pure", "pea"],
               "speciespea:block1_pur"=block1SpeciesEffs["block1", "pure", "pea"], 
               "speciespea:focal1_pur"=focal1, 
               "sigma_w"=truth[["sigma2_err_w"]],
               "sigma_p"= truth[["sigma2_err_p"]]),
      
      "lm"=c((summary(mod_w_pur)$coefficients)[,1],
             (summary(mod_p_pur)$coefficients)[, 1],
             sigma(mod_w_pur),sigma(mod_p_pur)))

```


## Mix + Pure 

### lmer :: Model 1 (Fixed effects + DGE + e)
```{r}
mod_w_mix <- lm(yield_1~1+block+ pea, data = droplevels(dat_mix[dat_mix$species=="wheat",]))
mod_p_mix <- lm(yield_1~1+block+ pea, data = droplevels(dat_mix[dat_mix$species=="pea",]))


cbind("true"=c("specieswheat_mix"=block1SpeciesEffs["mu", "mixed", "wheat"], 
               "specieswheat:block1_mix"=block1SpeciesEffs["block1", "mixed", "wheat"],
               "speciespea:neighbors1"=neighbors1,
               "speciespea_mix"=block1SpeciesEffs["mu", "mixed", "pea"],
               "speciespea:block1_mix"=block1SpeciesEffs["block1", "mixed", "pea"],

               "speciespea:focal1"=focal1,  
               "sigma_w"=truth[["sigma2_err_w"]],
               "sigma_p"=truth[["sigma2_err_w"]]),
      
      "lm"=c((summary(mod_w_mix)$coefficients)[,1],(summary(mod_p_mix)$coefficients)[, 1],
            sigma(mod_w_mix)^2,
             sigma(mod_p_mix)^2))
```


### TMB 

#### Mod 1 
pur : 
$$\mathbf{y}= X\mathbf{b}+ \mathbf{\epsilon}$$
mix : 
$$\mathbf{Y}= XB +\in$$


```{r}
model <- "
#include <TMB.hpp>
using namespace density;

template<class Type>
Type objective_function<Type>::operator() ()
{
  /*-------------------------------Data--------------------------------------*/
  // mix
  DATA_ARRAY(Ymix);                   //Yield for cereals and legumes in MS
  DATA_MATRIX(Xmix);                 // Design matrix for fixed effects in MS
  DATA_MATRIX(ZDl_mix);                 // Design matrix for fixed effects in MS
  DATA_MATRIX(Id_mix);            // Identity matrix for errors in mixed stand 

  // pure
  DATA_VECTOR(y_c);           // Yield in pure stand for cereal species
  DATA_VECTOR(y_l);         // Yield in pure stand for legume species
  DATA_MATRIX(X_c);       // Design matrix for fixed effects for cereal species
  DATA_MATRIX(X_l);     // Design matrix for fixed effects for legume species
  DATA_MATRIX(Idn_c); // Identity matrix for errors in cereal yield measurements 
  DATA_MATRIX(Idn_l);// Identity matrix for errors in legume yield measurements 
  
  /*-----------------------------------Parameters-----------------------------*/
  PARAMETER_VECTOR(beta);       // vector f=of fixed effects
  PARAMETER(log_sd_c);          // errors in cereal yield measurements 
  PARAMETER(log_sd_l);        // errors in legumes yield measurements 
  PARAMETER_VECTOR(log_sd_E_mix);      // Errors parameters for cereals and legumes species
  PARAMETER_VECTOR(unconstr_cor_E_mix); // Unconstraint correlation for errors
  
  
  /*----------------------------Local variales -------------------*/
  // size
  int d = 2; // number of species
  int n_1 = Ymix.rows(); // number of total mixed plots
  int n_c = y_c.size(); //length of cereals yield vector in pure
  int n_l = y_l.size(); // lentgh of legumes yield vector in pure
  int f_c = X_c.cols(); //number of fixed for cereals
  int f_l = X_l.cols(); //number of fixed effects for legumes
  int f_m = Xmix.cols(); // number of fixed effects in mixed stand
  int f = beta.size(); // total number of fixed effects
  
  
  /*---------------- DGE & fixed effects (local parameters)-------------------*/
  // b_c: vector of fixed effects : mu & block for cereals
  vector<Type> b_c(f_c);
  for (int i = 0; i < f_c; ++i) {
    b_c[i] = beta[i];
  }
  
  // b_l: vector of fixed effects : mu-block-DGE for legumes
  vector<Type> b_l(f_l);
  for (int i = 0; i < f_l; ++i) {
    b_l[i] = beta[i + f_c]; // Adjust index to start from 2 for the beta vector
  }
  
  
    // Matrix of pea DGE and IGE for pea
  matrix<Type> U_l(2, d);
  U_l.row(0) << beta[5], 0;                   // IGE of pea in the first col
  U_l.row(1) << 0, beta[4];                 // DGE of pea in the 2nd col
  
  
  //B_mix
  matrix<Type> B_mix(f_m, d);
  B_mix.row(0) << beta[6], beta[8];
  B_mix.row(1) << beta[7], beta[9];
 
 /*----------------------------Objective function-----------------------------*/ 
  Type nll = Type(0.0);
  
  
  /*----------------------------contribution to the nll-----------------------*/ 
  
  // Contribution of the cereals observation  in pure stand  to the nll
  vector<Type> m_c(n_c);
  m_c = X_c * b_c;
  MVNORM_t<Type> mvn_yc_cor(Idn_c);
  vector<Type> vec_sd_c(n_c);
  vec_sd_c.fill(exp(log_sd_c));
  nll += VECSCALE(mvn_yc_cor, vec_sd_c)(y_c - m_c);
  
  
  // Contribution of the legumes observation  in pure stand  to the nll
  vector<Type> m_l(n_l);
  m_l = X_l * b_l;
  MVNORM_t<Type> mvn_yl_cor(Idn_l);
  vector<Type> vec_sd_l(n_l);
  vec_sd_l.fill(exp(log_sd_l));
  nll += VECSCALE(mvn_yl_cor, vec_sd_l)(y_l- m_l);
  

  // Contribution of the observation in mix to the nll
  UNSTRUCTURED_CORR_t<Type> mvn_y_u(unconstr_cor_E_mix);   // d x d; unscaled
  vector<Type> sd_E_mix = exp(log_sd_E_mix);        // d x 1
  VECSCALE_t<UNSTRUCTURED_CORR_t<Type> > f_y = VECSCALE(mvn_y_u, sd_E_mix);// d x d
  MVNORM_t<Type> g_y(Id_mix);               //   n_1   x   n_1
  SEPARABLE_t< VECSCALE_t<UNSTRUCTURED_CORR_t<Type> > , MVNORM_t<Type> > h_Y(f_y, g_y);
  matrix<Type> M(Ymix.rows(), d);
  M = Xmix*B_mix + ZDl_mix*U_l;
  
  //nll
  nll += h_Y(Ymix - M.vec());
  
  /*----------------------------report correlation matrices------------------*/ 
  
  matrix<Type> Cor_E_mix(d,d);
  Cor_E_mix = mvn_y_u.cov();
  REPORT(Cor_E_mix);
  
  /*---------------------------reporting nll-------------------------------*/
  return nll;
}
"
dllID <- "TMB_full_lm_mod"
cat(model, file=paste0(dllID, ".cpp"))
if(! file.exists(paste0(dllID, ".so")))
  compile(paste0(dllID, ".cpp"))
dyn.load(dynlib(dllID))
```


Build object with  `MakeADFun` to combine the data, the parameters, and the model

```{r}
# Data & Parameters
Data = list( C = W, L=P,
             Ymix=Y_mix_1,Xmix=listZs[["Xmix"]], ZDl_mix=listZs[["ZDp_mix"]], Id_mix=diag(n_1),
             y_c =y_w_pur_1, X_c = listZs[["X_wheat_pur"]], Idn_c = Idn_w_pur,
             y_l =y_p_pur_1, X_l = listZs[["X_pea_pur"]], Idn_l = Idn_p_pur)


Parameters = list(
  beta = c(true_beta*0),
  log_sd_c = log(1),
  log_sd_l = log(1),
  log_sd_E_mix=rep(log(1),d),
  unconstr_cor_E_mix=rep(0, 1))


system.time(
  Obj <- MakeADFun(data=Data, parameters= Parameters,
                   checkParameterOrder=FALSE,
                  hessian=FALSE, DLL=dllID)
)
```

Fitting the model to data using `nlminb` , alternatively we can use `TMBhelper::fit_tmb`:
```{r}
system.time(
  Opt <- nlminb(start = Obj$par, # Initial values for the parameters
                objective = Obj$fn, # Function to be minimized
                gradient = Obj$gr) # Gradient of the objective
)
cat("\014");
```

######  Check

```{r}
Report = Obj$report()
sdrep <- sdreport(Obj)
sdr2pTmb <- summary(sdrep)
cat("\014");

```

Parameters
```{r}
# Parameters
fixed_effects <- as.numeric(sdr2pTmb[rownames(sdr2pTmb) == "beta", "Estimate"])
var_er_mix <- exp(as.numeric(sdr2pTmb[rownames(sdr2pTmb) == "log_sd_E_mix", "Estimate"]))^2
er_pur <-  exp(as.numeric(sdr2pTmb[c("log_sd_c", "log_sd_l"),"Estimate"]))^2
cor_E_U_estimate <- c(Report$Cor_E_mix[2])

params <- cbind("true"=c(
  "specieswheat_pur"=block1SpeciesEffs["mu", "pure", "wheat"],
  "specieswheat:block1"= block1SpeciesEffs["block1", "pure", "wheat"],
  "speciespea_pur"=block1SpeciesEffs["mu", "pure", "pea"],
  "speciespea:block1_pur"= block1SpeciesEffs["block1", "pure", "pea"],
  "speciespea:focal1"=focal1,
  "speciespea:neighbors1"= neighbors1, 
  
  "specieswheat_mix"=block1SpeciesEffs["mu", "mixed", "wheat"],
  "specieswheat:block1_mix"= block1SpeciesEffs["block1", "mixed", "wheat"],
  "speciespea_mix"=block1SpeciesEffs["mu", "mixed", "pea"], 
  "speciespea:block1_mix"=block1SpeciesEffs["block1", "mixed", "pea"],
  "cor_sigma_err_mix"=truth[["cor_E"]],
  "sigma_err_w_mix"=truth[["sigma2_err_w"]],
  "sigma_err_p_mix"=truth[["sigma2_err_p"]],
  "sigma_err_w_pur"=truth[["sigma2_err_w"]],
  "sigma_err_p_pur"=truth[["sigma2_err_p"]]),
                
                "TMB"=c(c(round(fixed_effects, 2), round(cor_E_U_estimate, 2),
                          round(var_er_mix,2),  round(er_pur, 2))))
params
```

std. error
```{r}
# Extracting standard errors
row_names<- c("beta", "log_sd_E_mix", "log_sd_c", "log_sd_l")
std.Error <- sdr2pTmb[rownames(sdr2pTmb) %in% row_names, "Std. Error"]
names(std.Error) <- rownames(sdr2pTmb)[rownames(sdr2pTmb) %in% row_names]

# Convert to data frame and assign column names
cbind( round(std.Error, 4))
```

# Appendix
print(sessionInfo(), locale=FALSE)

```{r info}
t1 <- proc.time(); t1 - t0
```
